Kepler's Demographic Cliff: Ages of Young Stars and Planets in the Kepler Field

### 2024-05-01 paper/ms.tex
update ms

\paragraph{NGC~6811}
\citet{Meibom_2013} reported the discovery of Kepler-66 and -67b, two
mini-Neptunes in NGC~6811 ($\approx$1\,Gyr).
We report rotation-based ages for these systems of
$1419^{+657}_{-353}$\,Myr and $873.75\pm{112}$\,Myr respectively.
For Kepler-66, $T_{\rm eff}$=5898\,K, and $P_{\rm
rot}$=10.25$\pm$0.10\,days.
{\it LGB TODO: check again after dereddening...}

>>>>

\paragraph{NGC~6811}
\citet{Meibom_2013} reported the discovery of Kepler-66 and -67b, two
mini-Neptunes in NGC~6811 ($\approx$1\,Gyr).  We report rotation-based
ages for these systems of \kepsixsixtgyro\ and \kepsixseventgyro\ for
Kepler-66 and -67b, respectively.  Kepler-66 ($T_{\rm
eff}$$\approx$5900\,K, $P_{\rm rot}$$\approx$10.4\,days) has a lower
precision and a more asymmetric posterior because the spindown rates
of stars this hot are relatively slow after the first gigayear.
Kepler-67 ($T_{\rm eff}$$\approx$5100\,K, $P_{\rm
rot}$$\approx$10.3\,days) is marginally hotter than the later K dwarfs
that have ``stalled'' spindown from 0.7 to 1\,Gyr, enabling its
rotation period to be diagnostic of the stellar age.
